### 2019-03-12 papers/journal/property.tex
added QBF section and attached Synthesis encodings to it
ads

The conjecture relates graph-connectedness to a particular variation of SNARE pairing and regulation rules of the VTS.
%
We are interested in the following two type of properties of the transport graph:

\begin{enumerate}
\item Existential condition:
%the structural connectedness of the transport graph required for the system driven by a particular set of rules. 
structural connectedness of a transport graph which satisfies the stated set of rules.

%there is a transport graph with the structural connectedness which satisfies the stated set of rules.

%that a transport graph satisfies driven by a particular set of rules. 
%And we are interested in the least one.

\item Universal condition: 
%every graph with the structural connectedness satisfies the stated set of rules. 
the structural connectedness that ensures every transport graph with that fundamental structure satisfies the stated set of rules. 
%The goal is to find the minimum graph connectivity that satisfies sufficient condition.
\end{enumerate}

The goal is to find the minimum graph connectivity that satisfies each of these condition.

%We express both these conditions as assertions in our program.

\subsubsection{Checking existential conditions} 
In our program, the rules VTS needs to follow 
%
%are we represent the stability, fusion, SNARE pairing and regulation rules, and the connectedness property that the system needs to follow, as 
%
are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
%
Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
%
We use these functions to define the assertion that characterizes the existential condition to be checked. 
%
We will show in later sections how we encode these Boolean functions.

To ensure that k-connectedness is an existential condition, we have to find a k-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also have to ensure that the particular k is the least one. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph (G) we specify our property as a query for the existence of a model for a conjunction of the formula representing stability, fusion and specific graph connectivity constraint. 
%

\begin{align*}
  &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)} 
\end{align*}

We will start with the value of k = 1 and check for the satisfiability of the above formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of k. 
%
If the formula is not satisfiable we increment the k by 1 and perform the same procedure. 
%
In this way, we ensure that the reported k is the minimum connectivity of the VTS that satisfies the existential condition.  
% Used E as edge and L_e L_n as label for node and the edge,

\subsubsection{Checking universal conditions}

Similarly, for the conjecture that k-connectedness is a universal condition for the VTS, we have to ensure that every graph of k-connected structure satisfies all the rules (and constraints) of the system. 
%
We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system.

\begin{align*}
  & \forall G \, \texttt{Connectivity(k)} \implies  \exists
                        f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
\end{align*}

Note that the specification of this requires quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas. 
%
%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
We will use the same procedure as the existential condition to ensure the k to be the least one.

>>>>

We analyze the model against our desired properties.
%
Since in biology there are are no declared specifications or properties,
we conjecture some properties that appear to be true in all known
biological systems.
%
In this paper, we choose graph connectedness to be a key property.
%
We will also seek two kinds of questions give the property.

% %
% In this paper,
% our conjecture relates graph-connectedness to a particular variation of SNARE pairing and
% regulation rules of the VTS.
% %
% We are interested in the following two type of properties of the transport graph:

\begin{enumerate}
\item {\em Existential condition:}
if there is a VTS that satisfies the connectedness property.

\item {\em Universal condition:}
  if there is a connectedness property that is satisfied by each valid VTS.
\end{enumerate}

The goal is to find the minimum graph connectivity properties that for each of the condition.

% In our program, the rules VTS needs to follow 
% %
% are represented as constrained over the transport graphs (G), label on the nodes and edges and activity of those labels (determined by a Boolean function f). 
% %
% Each of these constrained functions is defined to be TRUE for a G and f: if and only if the corresponding condition holds for the given G and f. 
% %
% We use these functions to define the assertion that characterizes the corresponding condition to be checked. 
% %
% We will show in later sections how we encode these Boolean functions.

\subsubsection{Search for existential condition} 
%
% To ensure that k-connectedness is an existential condition,
%
We need to find a $k$-connected graph that satisfies all the rules (and constraints) of the system. 
%
We also aim to find the minimum $k$. 
%
%Let's fix our conjecture: ``k-connectedness is a necessary condition for the system regulated by a Boolean function on the node and SNARE-SNARE inhibition on the edge". 
%
To find a k-connected graph we specify our property as a query for the existence
of a model for a conjunction of the formula representing stability, fusion and specific
graph connectivity constraint. 
%
% \begin{align*}
%   &\texttt{LabeledVTS} = \texttt{Stability} \, \land \, \texttt{Fusion} \land \, \texttt{MinConnectivity(k)}
%  \tag{E}\label{eq:existcond}
% \end{align*}
%
We will start with the value of $k = 1$ and check for the satisfiability of the formula.
%
In case the formula is satisfiable the procedure terminates and we report the value of $k$. 
%
If the formula is not satisfiable we increment the $k$ by $1$ and perform the same procedure. 
%
In this way, we ensure that the reported $k$ is the minimum connectivity of the VTS that
satisfies the existential condition.
%
% Used E as edge and L_e L_n as label for node and the edge,

\subsubsection{Search for universal problem}
%
% Similarly, for the conjecture that k-connectedness is a universal condition for the VTS,
For some $k>0$,
we have to ensure that every graph of $k$-connected structure satisfies all
the rules of the system.
%
We also aim to find the minimum $k$. 
% We also have to ensure that the particular k is the least one. 
%
This condition can be specified as: for every k-connected graph, there exists a satisfiable assignment following the rules of the system. 
%
% \begin{align*}
%   & \forall G \, \texttt{Connectivity(k)} \implies  \exists
%                         f,p: \texttt{Stability} \, \land \, \texttt{Fusion}  
%   \tag{U}\label{eq:univcond}
% \end{align*}
%
We will use the same procedure as the existential condition to ensure the k to be the least one.
%
The formula for the problem has quantifier alternation. 
%
Most SAT solvers can check (at least efficiently) only quantifier-free formulas.
%
We need a QBF solvers for such queries.
%
%To handle this challenge, we used a combination of nondeterminism and Boolean enumeration at the C-source level to eliminate quantifiers, as explained further below.
